%\documentclass[../thesis.tex]{subfiles}
%\begin{document}
%\item \fullcite{Hershey2011}
%\item \fullcite{Hershey2016}
%\item \fullcite{Xu2016}
%\item \fullcite{Hershey2017}
%\item \fullcite{Bangsund2018}
%\item \fullcite{Bangsund2018a}



\subsection*{Journal Publications}
\begin{itemize}
\item J Bangsund, \textbf{KW Hershey}, RJ Holmes. {\em Origin of Lifetime Enhancement in Mixed Emissive Layer Organic Light-Emitting Devices} ACS Applied Materials and Interfaces. 2018.
\item  \textbf{KW Hershey}, J Suddard-Bangsund, G Qian, RJ Holmes. {\em Decoupling Degradation in Exciton Formation and Recombination During Lifetime Testing of Organic Light-Emitting Devices}. Applied Physics Letters. 2017.
\item F Xu, \textbf{KW Hershey}, RH Holmes, TR Hoye. {\em Blue-Emitting Arylalkynyl Naphthalene Derivatives via a Hexadehydro-Diels-Alder Cascade Reaction} . Journal of the American Chemical Society. 2016.
\item \textbf{KW Hershey}, RJ Holmes. {\em Unified Analysis of Transient and Steady-State Electrophosphorescence Using Exciton and Polaron Dynamics Modeling} . Journal of Applied Physics. 2016.
\item \textbf{KW Hershey}, JP Cottingham. {\em Matierial Properties of Pipes of Reeds From the Southeast Asian Khaen} . Journal of the Acoustics Society of America. 2011.
\end{itemize}



\subsection*{Oral Presentations}
\begin{itemize}
\item \textbf{KW Hershey}, RJ Holmes.{\em Decoupling Exciton Formation and Recombination Losses in Organic Light-Emitting Devices During Lifetime Testing}, Optical Society of America - Light, Energy and the Environment Congress. Boulder, CO. November 2017
\item \textbf{KW Hershey}, RJ Holmes.{\em Decoupling Degradation Mechanisms During Lifetime Testing of Organic Light-Emitting Devices}, UMN IPrime. Minneapolis, MN. June 2017 
\item \textbf{KW Hershey}, RJ Holmes.{\em Modeling Exciton and Polaron Dynamics to Analyze OLED Behavior}, UMN IPrime. Minneapolis, MN. June 2016 
\item \textbf{KW Hershey}, RJ Holmes.{\em Modeling Exciton and Polaron Dynamics to Analyze OLED Behavior}, MRS Spring Conference. Phoenix, AZ. April 2016 
\item \textbf{KW Hershey}, JP Cottingham. {\em Material Properties of Pipes and Reeds from the Southeast Asian Khaen}, Acoustical Society of America National Meeting. Seattle, WA. May 2011 
\end{itemize}

\subsection*{Poster Presentations}
\begin{itemize}
\item \textbf{KW Hershey}, RJ Holmes.{\em Decoupling Degradation Mechanisms During Lifetime Testing of Organic Light-Emitting Devices}, UMN IPrime. Minneapolis, MN. June 2017 
\item \textbf{KW Hershey}, RJ Holmes.{\em Connecting Transient and Steady-State Dynamics in Organic Light Emitting Devices}, UMN IPrime. Minneapolis, MN. June 2016 
\item \textbf{KW Hershey}, RJ Holmes.{\em Transient Analysis of Organic Light-emitting Devices}, UMN IPrime. Minneapolis, MN. May 2015 
\item \textbf{KW Hershey}, JP Cottingham.{\em Material Properties of Pipes and Reeds from the Southeast Asian Khaen}, Sigma Pi Sigma Quadrennial Physics Congress. Orlando, FL. April 2012.
\end{itemize}



%\end{document}
